Machine Learning - Exercise 3

### 2021-02-21 exercise_3/paper/paper_ex3.tex

@@

       As mentioned in the beginning of Section~\ref{sec:copycat} Azure could not recognise all of the faces in our data set and hence could not classify for each face an emotion. Therefore, we added to the 8 emotions a further class called 'no\textunderscore face'. Figure~\ref{subfig:emotions_original-labels} shows the proportion of the different classes in our data set. In Figure~\ref{subfig:emotions_azure-labels} the distribution after classification by Azure. As one can see Azure could not detect about $13\%$ of the human faces.

@@

        %Originally, we wanted to add instances, which are not part of the problem domain to our fake data set. However, as Azure does not classify images in which it does not detect any face, this was not possible.

@@

        Figure~\ref{fig:performance-azure} shows the results of our tests. Overall it can be seen that the accuracy as well as the equality improve for larger training sets. The best value for the accuracy in our tests was $0.578$. which seems much better compared to the results from the paper with about $0.35$. We also computed the accuracy of the Azure Emotion API on the test set and obtained an accuracy of $0.764$.

        However, the extracted model using the whole training set was was able to coincide on $70\%$ on the test data.

@@

        We took the offer for students and got $100$\$ of credit for free, which we used for the standard option. Therefore, we could label up to $10$ images per second but had to pay $0.01$\$ per $1\,000$ calls.

@@

@@

        Furthermore, we will consider the equality of our extracted model. In Figure~\ref{fig:equality_cat} we can see that graph for both approaches looks very similar.

@@

        It is visible, that in case of the attack set being of similar size the attack set consisting only of instances, that are part of the problem domain performed better.

        Once again using only problem domain data performed better, when looking at attack sets of similar size.

                %the number of instances in the attack set has more visible influence on the accuracy of the extracted model. The accuracy increases from $0.673$ to $0.791$.

    The time needed to train the models grew roughly linearly with the size of the attack sets. The largest attack set of size $94\,572$ trained the extracted model in roughly $24$ minutes. Below is the time needed to construct the extracted model compared to the size of the attack set.
        \begin{figure}[h!]
            \centering      \includegraphics[width=0.6\textwidth]{exercise_3/paper/images/Time_copy_cat.png}
            \caption{Time needed to extract a model}
            \label{fig:time_cat}
        \end{figure}

        ------------------------------------------------------------------

        We tested the accuracy of the set by mixing the cat data set and the Stanford dog data set and picking $7\,644$ random images out of it. The resulting accuracy was $0,821$.

\section{Decision Tree Path-Finding Attack}
    As the name suggests this model stealing attack targets decision tree models. Such a model divides the input space into several discrete partitions. The idea behind the decision tree path-finding attack is to vary the values of each feature bit by bit to find the value at which the tree splits. Algorithm~\ref{alg:DT-attack} you can find a rough sketch of this attack. In this pseudocode let $Q$ be the set of unprocessed queries and $P$ the set of explored leaves with their classification.

    \begin{algorithm}
        \caption{Path-finding attack for decision trees}
	    \begin{algorithmic}[1]
%		    \State Let $Q$ be the set of unprocessed queries;
%		    \State Let $P$ be the set of explored leaves with their classification;
		    \State Add a random first query to $x_{init}$ to $Q$;
		    \State While $Q\neq\emptyset$ process $x\in Q$;
		    \State Do binary search over the continous features and check whether a new leaf can be discovered;
		    \State in this way explore the continuous features and variate the discrete features to find all leaves;
	    \end{algorithmic}
	    \label{alg:DT-attack}
    \end{algorithm}
    A weakness of this approach is that if two instances that lead to different leaves that are classified as the same, only differ in a single feature, the difference may not be registered in the extracted model.

@@

    \subsection{Models}
        Since this extraction method does not use data sets to get the model to confess its knowledge, we instead look at publicly available decision tree models from bigml which we are looking to extract.
        \subsubsection{US IRS 2008 tax data patterns}
        https://bigml.com/user/francisco/gallery/model/50c008bb3b56351981000375
        This decision tree was generated using data from tax returns filed in the US in 2009. The decision tree aims to predict the home state of the tax payer.
        \subsubsection{Steak survey}
        https://bigml.com/user/ashikiar/gallery/model/537be4c3d9949779990041e9
        This model was based on data from a \hyperlink{https://fivethirtyeight.com/features/how-americans-like-their-steak/}{FiveThirtyEighty survey}, which asked a lot of general questions as well as how they liked their steak prepared (Rare, Medium-rare, Medium, Medium-well, Well). 
        \subsubsection{Bitcoin price} 
        https://bigml.com/user/czuriaga/gallery/model/51ccb90a035d07603900039e
        Was macht der TREEEE?????
        \subsubsection{Email Importance}
        https://bigml.com/user/louisdorard/gallery/model/52fa8aa60c0b5e6d4a0030c1

        This model was built using Email data collected from the users own inbox. The importance was set by Gmail. Using a variety of features including length of the mail and whether the mail was sent by a contact, the tree classifies the importance.
        \subsubsection{gss survey}
        Find das model ned
        \subsubsection{med price}
        Find ich ned
    \subsection{Evaluation}
        ...

@@

\bibliographystyle{abbrv}
\bibliography{literature}

>>>>

%%%%%%%% Biblatex
\usepackage[backend=biber,style=numeric,sortlocale=de_DE,natbib=true,url=false, doi=true,eprint=false]{biblatex}
\addbibresource{literature.bib}

@@

       As mentioned in the beginning of Section~\ref{sec:copycat} Azure could not recognise all of the faces in our data set and hence could not classify for each face an emotion. Therefore, we added to the 8 emotions a further class called 'no\textunderscore face'. Figure~\ref{subfig:emotions_original-labels} shows the proportion of the different classes in our data set. In Figure~\ref{subfig:emotions_azure-labels} the distribution after classification by Azure. As one can see Azure could not detect about $13\%$ of the human faces. We only performed a copycat attack with a problem domain dataset for this reason, since the Azure Emotion API in the current version does not allow us to extract emotions for images without an detected face.

@@

@@

        Figure~\ref{fig:performance-azure} shows the results of our tests. Overall it can be seen that the accuracy as well as the equality improve for larger training sets. The best value for the accuracy in our tests was $0.578$ which seems much better compared to the results from the paper with about $0.35$ depending on the attack data set. Nevertheless, the Azure Model used in the paper (which was an older version) also had an accuracy of around $0.351$. We also computed the accuracy of the Azure Emotion API on the test set and obtained an accuracy of $0.764$, which is much better than the accuracy recorded in the paper. Therefore our performance was $0.756$ compared to the target network.

        The extracted model using the whole attack set was was able to coincide on $70\%$ with the azure classifications on our test set.

@@

        We took the offer for students and got $100$\$ of credit for free, which we used for the standard option. Therefore, we could label up to $10$ images per second but had to pay $1$\$ per $1\,000$ calls.

@@

        The accuracy of the target model on the same test set was $0,821$. 
        Comparing the accuracy of the extracted models in our tests to the accuracy of the target CNN we can see that this measure is very close to the original one.

@@

        Furthermore, we will consider the equality of our extracted model. In Figure~\ref{fig:equality_cat} we can see that the two graphs for both approaches look very similar. For a larger attack set the equality can be improved up to $0.864$. This means, compared to the previous Emotion Detection problem, we were able to copy the model in this setting better in these tests and on the given data.

@@

        In addition to that, we will also look at how much time it takes to train the extracted model for an attack set of certain size. As it can be seen in Figure~\ref{fig:time_cat} the time for training the models grew roughly linear with the size of the attack set in our tests. The largest attack set containing $94\,572$ images needed about $24$ minutes to perform the attack, i.e. to build the extracted model.

        \begin{figure}[h!]
            \centering      \includegraphics[width=0.65\textwidth]{exercise_3/paper/images/Time_copy_cat.png}
            \caption{Time needed to extract a model}
            \label{fig:time_cat}
        \end{figure}

        Summarizing it can be said that for a fixed number of PD data, adding NPD images improves the accuracy and equality of the extracted model. But since more queries to the target network are required when adding NPD data, the time needed for building the model increases. Hence, there is a trade-off between the performance of the model and the costs.

\section{Decision Tree Path-Finding Attack}
    As the name suggests this model stealing attack targets decision tree models. Such a model divides the input space into several discrete partitions. The idea behind the decision tree path-finding attack is to vary the values of each feature bit by bit and then to query the black-box to find the values at which the tree splits. In Algorithm~\ref{alg:DT-attack} you can find a rough sketch of this attack. In this pseudocode let $Q$ be the set of unprocessed queries and $P$ the set of explored leaves with their classification value.

    \begin{algorithm}
        \caption{Path-finding attack for decision trees}
	    \begin{algorithmic}[1]
%		    \State Let $Q$ be the set of unprocessed queries;
%		    \State Let $P$ be the set of explored leaves with their classification;
		    \State Add a random first query to $x_{init}$ to $Q$;
		    \State While $Q\neq\emptyset$ process $x\in Q$;
		    \State Do binary search over the continous features and check whether a new leaf can be discovered;
		    \State in this way explore the continuous features and variate the discrete features to find all leaves;
	    \end{algorithmic}
	    \label{alg:DT-attack}
    \end{algorithm}

    A weakness of this approach is that for two instances which e.g. only differ in a single feature, the target decision tree leads to different leaves which are classified as the same, the difference may not be registered in the extracted model.

@@

    \subsection{Models}
        Since this model stealing attack does not use attack sets to get the model (like the previous one) to confess its knowledge, we looked at publicly available decision tree models from BigML instead of data sets.

        Moreover, we decided to consider the models from the paper to find out if this model stealing attack implemented exactly as in the paper but performed in a different setting yields to exactly the same extracted model or if it leads to any differences.

        \subsubsection{US IRS 2008 tax data patterns}
            The decision tree for US IRS 2008 tax data patterns~\cite{tax} was generated using data from tax returns filed in the US in 2008. The decision tree aims to predict the home state of the tax payer depending, e.g. on the unemployment compensation, real estate taxes or the tax due at time of filing.

        \subsubsection{Steak survey}

            This model was based on data from a \hyperlink{https://fivethirtyeight.com/features/how-americans-like-their-steak/}{FiveThirtyEighty survey}, which asked a lot of general questions as well as how they liked their steak prepared (Rare, Medium-rare, Medium, Medium-well, Well).

        \subsubsection{Bitcoin price} 
            https://bigml.com/user/czuriaga/gallery/model/51ccb90a035d07603900039e
            Was macht der TREEEE?????

        \subsubsection{Email Importance}
            https://bigml.com/user/louisdorard/gallery/model/52fa8aa60c0b5e6d4a0030c1

            This model was built using Email data collected from the users own inbox. The importance was set by Gmail. Using a variety of features including length of the mail and whether the mail was sent by a contact, the tree classifies the importance.

        \subsubsection{gss survey}
            Find das model ned

        \subsubsection{med price}
            Find ich ned

    \subsection{Evaluation}
        ...

@@

\printbibliography
